Probabilistic Automated Language Learning for Configuration Files

### 2016-05-01 OSDI/limit.tex
config: related work and limitation sec

>>>>

This section discusses a few \app's limitations
and possible solutions.

\para{Legal misconfigurations.}
While \app can check diverse configuration errors without
human participations, all the misconfiguration detection techniques,
including \app, cannot handle some types of configuration errors
resulting from events occurred during system runtime.
Such configuration errors are referred to as {\em legal misconfigurations}%
~\cite{yin11anempirical}. As shown in Yin {\em et al.}%
~\cite{yin11anempirical}, many parameter misconfigurations have 
perfectly legal parameters but do not deliver the functionality intended
by users. These cases are more difficult to detect by
automatic checkers and may require more user training or
better configuration design.
A potential solution is to combine existing misconfiguration diagnosis
tools, \eg, X-ray~\cite{}, with \app in order to enhance the 
misconfiguration checking capability.

\para{}

### 2016-05-01 OSDI/rel.tex
config: related work and limitation sec

Several machine learning-based misconfiguration detection efforts 
also have been proposed~\cite{yuan11context, zhang14encore}.
Specifically, EnCore~\cite{zhang14encore} introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that enforce learning to focus on patterns of interests.
By this way, EnCore filters out irrelevant information and reduces
the false positives; moreover, the templates are able to express
system environment information that state-of-the-art machine learning
techniques cannot handle.
Compared with EnCore, which focuses on a specific type of
misconfiguration, \app is capable of tackling more general configuration
errors.

>>>>

Several machine learning-based misconfiguration detection efforts 
also have been proposed~\cite{yuan11context, zhang14encore}.
Specifically, EnCore~\cite{zhang14encore} introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that enforce learning to focus on patterns of interests.
By this way, EnCore filters out irrelevant information and reduces
the false positives; moreover, the templates are able to express
system environment information that state-of-the-art machine learning
techniques cannot handle.
Compared with EnCore, \app has the following advantages.
First, \app does not rely on whether the files in given configuration set 
are 100\% correct. Second, \app can cover much more types of 
misconfigurations, since \app introduces probabilistic type checking
mechanism. Finally, \app is a language framework, which could 
even be used to write configuration files, but EnCore is only a 
misconfiguration detection tool.
